Supplementary Material

### 2022-01-28 supplement/supplement.Rmd
CD revision 1, integrate coauthor feedback

```{r sitables7, tab.id="sitables7", tab.cap="Correlations and descriptive statistics for witnessing and involvement in fights and perceived neighborhood violence. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
si_table.07.0 %>% 
  flextable() %>% 
  set_header_labels(Variable = "") %>% 
  set_table_properties(width = 1, layout = "autofit") %>% 
  add_footer_row(
    values = " ",
    colwidths = 4
  ) %>% 
  add_footer_row(
    values = " ",
    colwidths = 4
  ) %>% 
  compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
    part = "footer"
  ) 
```

>>>>

```{r sitables7, tab.id="sitables7", tab.cap="Correlations and descriptive statistics for witnessing and involvement in fights and perceived neighborhood violence."}
si_table.07.0 %>% 
  flextable() %>% 
  set_header_labels(Variable = "") %>% 
  set_table_properties(width = 1, layout = "autofit") %>% 
  add_footer_row(
    values = " ",
    colwidths = 4
  ) %>% 
  add_footer_row(
    values = " ",
    colwidths = 4
  ) %>% 
  compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), as_i("* p "), "< .05, ", as_i("** p "), "< .01"), 
    part = "footer"
  ) 
```
